\section*{History}

\paragraph*{Version 1.0: July, 2017.}
\begin{itemize}
  \item Supported the Fortran2008 features.
  \item Corrected the descriptions on the current specification.
  \begin{itemize}
    \item Corrected the description on the I/O specifier.\newline
          (wrong) value attribute \newline (correct) child element
    \item Added the missed attribute {\tt is\_assumed\_shape} to the {\tt indexRange} element.
  \end{itemize}
\end{itemize}

%\paragraph*{Version 1.2.1: November, 2014.} Corrections and
%clarifications to Version 1.2.
%
%\begin{itemize}
%  \item \ref{sub:align} {\tt align} Directive
%  \item \ref{sub:loop_construct} {\tt loop} Directive
%  \item \ref{173311_31Oct14} {\tt [C]} Declarations of Coarrays
%  \item \ref{172700_31Oct14} {\tt [F] local\_alias} Directive
%  \item \ref{173437_31Oct14} Array Section Notation
%  \item \ref{sec:Array assignment statements in C} Array Assignment Statement
%
%\end{itemize}
%
%\paragraph*{Version 1.2: November 20, 2013}
%
%\paragraph*{Version 1.1: November 13, 2012}
%
%\paragraph*{Version 1.0: November 14, 2011}

\paragraph*{Version 0.9J: March 31, 2011}

\begin{itemize}
  \item Added the {\tt FassignStatement} element.
  \item Added the {\tt FpointerAssignStatement} element.
  \item Deleted the {\tt assignExpr} element.
  \item Deleted the {\tt FpointerAssignExpr} element.
  \item Deleted the {\tt assignExpr} element and {\tt FpointerAssignExpr} elements in the {\tt exprModel} model.
  \item Added the {\tt FassignStatement} and {\tt FpointerAssignStatement} elements to the {\tt statementModel} model.
  \item Added the {\tt is\_assumed\_size} attribute to the {\tt indexRange} element.
  \item Added the {\tt is\_intrinsic} attribute to the {\tt functionCall} element.
  \item Updated the description on the {\tt statementLabel} element.
  \item Support for {\tt coarray}.
  \begin{itemize}
    \item Modified the {\tt FbasicType} element.
    \item Added the {\tt coShape} element.
    \item Added the {\tt FcoArrayRef} element.
    \item Modified the {\tt varRef} element.
    \item Modified the {\tt alloc} element.
    \item Added the {\tt FcoArrayRef} element to the {\tt exprModel} model.
  \end{itemize}
\end{itemize}

