\section{ {\tt globalDeclarations} element}

The {\tt globalDeclarations} element is used for declaring global variables in the program and defining functions. The element has the following elements:

\begin{itemize}
\item {\tt functionDefinition} element - used to define functions,
\item {\tt varDecl} element - used to define variables,
\item {\tt functionDecl} element - used to declare functions, and
\item {\tt text} element - used to specify arbitrary text, such as directives.
\end{itemize}


\subsection{ {\tt functionDefinition} element}

The {\tt functionDefinition} element is used to define functions. 
The element has the following elements:

\begin{itemize}
\item {\tt name} element - specifies the function name,
\item {\tt symbols} element - specifies the parameter symbol list,
\end{itemize}

The symbols element specifies the symbol table for the corresponding parameters.

\begin{itemize}
\item {\tt params} element - used to define parameters, and
\item {\tt body} element - includes text for the {\tt functionDefinition} element within the body of the function. The {\tt functionDefinition} element within the body element indicates nested GCC functions. 
\end{itemize}

The element has the following attribute:

\begin{itemize}
\item {\tt is\_gccExtension} attribute.
\end{itemize}


\subsection{ {\tt params} element}

The {\tt params} element specifies a list of parameters for the function.

\begin{itemize}
\item {\tt name} element - specifies the name elements corresponding to the parameters.
\item {\tt ellipsis} - indicates variable length parameters. This element can be specified for the last subelement of the params element.
\item The name elements within the {\tt params} element must be ordered according to the parameter sequence. If there is data type information for a parameter, specify it using the {\tt type} attribute of the {\tt name} element. 
\end{itemize}


\subsection{ {\tt varDecl} element}

The {\tt varDecl} element is used to declare variables. Use the {\tt name} element to specify the names of identifiers used in function declarations. The element has the following elements:

\begin{itemize}
\item {\tt name} element - specifies the {\tt name} element corresponding to the function to be declared.
\item {\tt value} element - specifies an initial value for the variable. Use the {\tt value} element to specify initial values for arrays and structures, using multiple expressions.
\end{itemize}

\subsubsection*{Example}
\vspace{1mm}

\begin{CExample}
  int a[] = { 1, 2 };
\end{CExample}
\vspace{1mm}

\begin{XcodeMLExample}
  <varDecl>
    <name>a</name>
    <value>
      <intConstant type="int">1</intConstant>
      <intConstant type="int">2</intConstant>
    </value>
  </varDecl>
\end{XcodeMLExample}


\subsection{ {\tt functionDecl} element}

The {\tt functionDecl} element is used to declare functions. 
The element has the following element:

\begin{itemize}
\item {\tt name} element - specifies the function name.
\end{itemize}


